The development of children's ability to track and predict turn structure in conversation

### 2016-02-01 paper/Letters/ResponseLetter-Jan2016.tex

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

\opening{Dear Profs.  Dr. Gerrig and Dr. Pickering,}

\smallskip

\noindent I hereby resubmit a manuscript on ``The development of children's ability to track and predict turn structure in conversation'' to the \textit{Journal of Memory and Language}. Please note that Prof. Dr. Pickering has volunteered to continue handling this revised manuscript.

\noindent I apologize for our delay in getting the manuscript resubmitted. It took quite a long time to implement one of the suggestions from Reviewer 3, mostly because I had to acquire some new technical skills in order to carry out his/her suggested analysis on our computation-heavy data set. Nevertheless, I believe that the added analysis has substantially strengthened the paper as a whole, so I appreciate your patience very much.

\noindent Since our last submission, we have done quite a lot of work to improve our paper by addressing the reviewers' comments. For example, in addition to the new random permutation analysis suggested by Reviewer 3 (mentioned above), we have also included two further follow-up analyses in the Appendix (including additional experimental data), each inspired by the other reviewers' comments. We have also tried to make the text much more succinct, with separate and straightforward sections for the results and discussions, following requests from all three reviewers.

\noindent We hope that, with these changes, we have greatly improved the paper's quality. Please find a description of the specific comments addressed below. Thank you very much for your reconsideration. Please let us know if there is any further information that you require about the submission.

@@

\textbf{Manuscript identifying details:}

\begin{tabular}{ll}
\textit{ID:} & JML-14-235R2 \\
\textit{Title:} & The development of children's ability to track and \\
& predict turn structure in conversation \\
\textit{Authors:} & Marisa Casillas\textsuperscript{a} and Michael C. Frank\textsuperscript{b} \\
\textit{Affiliations:} & a) Max Planck Institute for Psycholinguistics and \\
& b) Stanford University
\end{tabular}

%----------------------------------------------------------------------------------------
\newpage
%----------------------------------------------------------------------------------------

\noindent We thank all three reviewers for their thorough and helpful comments on the previously submitted manuscript. We have tried to address all of their comments, both in the manuscript and here in the response letter.

### 2016-02-01 paper/CasillasFrank-Anticip.tex
Minor changes to cover letter, manuscript title page, and highlights.

\author[MPI]{Marisa Casillas\corref{cor1}}
\address[MPI]{Max Planck Institute for Psycholinguistics, Nijmegen}
%\address[StanfordLX]{Department of Linguistics, Stanford University}
\cortext[cor1]{Corresponding author}

@@

\begin{keyword}
Turn taking \sep Conversation \sep Development \sep Prosody \sep Questions \sep Eye-tracking
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

@@

\bigskip
\noindent \textbf{Methods}
\medskip

>>>>

\author[MPI]{Marisa Casillas\corref{cor1}}
\address[MPI]{Max Planck Institute for Psycholinguistics, Nijmegen}
%\address[StanfordLX]{Department of Linguistics, Stanford University}
\cortext[cor1]{Corresponding author. \\ Address: Wundtlaan 1, 6525 XD, Nijmegen, The Netherlands\\ Email: marisa.casillas@mpi.nl \\Telephone: +31 024 3521 566; Fax: +31 024 3521 213}

@@

\begin{keyword}
Turn taking \sep Conversation \sep Development \sep Questions \sep Eye-tracking \sep Anticipation
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

@@

\newpage
\noindent \textbf{Methods}
\medskip
